### 2023-12-03 main.tex
l

where $\Delta_{x,y}(C)$ denotes a copy of $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.

@@

$(\mathbf{a}^{+})_{a}^{u(x)}$ denotes a copy of $\mathbf{a}^{+}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\

@@

We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain  
\begin{equation}\label{transpositionPropertyH}
    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}
	%\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
	\dt
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C)$. Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in {gl}(N)$ the following holds:
\begin{equation}
 \text{if } \quad	[C,E]=0\qquad  \text{ then }\qquad \left[\Delta (C),\Delta(E)) \right]=0\dt
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=1}^{N-1}E_{aN}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta_{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta_{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $\mathcal{H}_{x,y}$. Exploiting these considerations we may write

@@

that is a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$. 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
which is a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find when $\nu>1$. We give 

>>>>

where $\Delta_{x,y}(C)$ denotes  $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.

@@

$(\mathbf{a}^{+})_{a}^{u(x)}$ denotes  $\mathbf{a}^{+}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\

@@

We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain  
\begin{equation}\label{transpositionPropertyH}
    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}
	%\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
	\dt
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C)$. Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in {gl}(N)$ the following holds:
\begin{equation}
 \text{if } \quad	[C,E]=0\qquad  \text{ then }\qquad \left[\Delta (C),\Delta(E)) \right]=0\dt
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=1}^{N-1}E_{aN}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta_{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta_{x,y}(E)$ denotes the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $\mathcal{H}_{x,y}$. Exploiting these considerations we may write

@@

to denote $\mathcal{S}_{1}$ (see \eqref{S1Gen}) when acting at site $x$. 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
whichdenotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probabilities are hard to find when $\nu>1$. We give 
